Supplement to Automatic Matching of Bullet Lands

### 2015-12-31 imaging-supplement.Rnw
first overview of unaligned signatures

\newpage
\section{One-on-one comparison of Hamby study}\label{supp:extended}
\hh{
add: we could extend the results of the James Hamby study by trying to match every single land against all other lands. This would almost double the number of comparisons ($21,115 = (118+88)\cdot 205/2$).  
}
\hh{Show aligned signatures for all ten barrels. }
<<aligned, echo=FALSE>>=
matches <- read.csv("csvs/matches.csv", header = FALSE)
matches$barrel <- rep(1:10, each=6)
matches$id <- 1:nrow(matches)
library(reshape2)
mm <- melt(matches, id.var=c("barrel", "id"), na.rm=TRUE)
mm <- subset(mm, value != "")
mm$value <- gsub("Br. Bullet ", "", mm$value)

@
\bibliographystyle{imsart-nameyear.bst}
%\biboptions{authoryear}
\bibliography{references}

>>>>

\newpage
\section{One-on-one comparison of Hamby study}\label{supp:extended}
\hh{
add: we could extend the results of the James Hamby study by trying to match every single land against all other lands. This would almost double the number of comparisons ($21,115 = (118+88)\cdot 205/2$).  
}
\hh{Show aligned signatures for all ten barrels. }
<<aligned, echo=FALSE, warning=FALSE, fig.width=8, fig.height=10, out.width='\\textwidth', cache=TRUE>>=
matches <- read.csv("csvs/matches.csv", header = FALSE)
matches$barrel <- rep(1:10, each=6)
matches$id <- 1:nrow(matches)
library(reshape2)
mm <- melt(matches, id.var=c("barrel", "id"), na.rm=TRUE)
mm <- subset(mm, value != "")
mm$value <- gsub("Br.* Bullet ", "", mm$value)
mm$prefix <- sprintf("Br%d Bullet ", mm$barrel)
unkns <- grep("[A-Z]",mm$value)
mm$prefix[unkns] <- "Ukn Bullet "
mm$path <- "~/papers/2015-imaging-paper/app/images/Hamby252_3DX3P1of2//"
mm$path[unkns] <- "~/papers/2015-imaging-paper/app/images/Hamby252_3DX3P2of2//"
mm$path <-   with(mm, paste0(path, prefix, value, ".x3p"))

ccs <- read.csv("csvs/crosscuts-25-new.csv")
mm <- merge(mm, ccs, by="path", all=TRUE)
mm <- subset(mm, !is.na(mm$cc))

crosscuts <- plyr::ldply(
  1:nrow(mm), 
  function(i) {
    dframe <- get_crosscut(mm$path[i], mm$cc[i])
    groove <- get_grooves(dframe)
    data.frame(mm[i,], fit_loess(dframe, groove)$resid$data)
  })
qplot(x=y, y=resid, data=crosscuts, geom="line", group=path) + ylim(c(-7,7)) + facet_wrap(facets=~id, ncol=6) + theme_bw() 
@
\bibliographystyle{imsart-nameyear.bst}
%\biboptions{authoryear}
\bibliography{references}
